Tropical Mathematics and the Lambda Calculus

### 2023-01-21 section2.tex
commit

Yet, what if these polynomials were tropical ones, i.e.~piecewise linear functions? This way, eq.~\eqref{eq:taylor} could really be interpreted as a decomposition of $\lambda$-terms via Lipschitz maps. In other words, unbounded term application could be seen 
as a limit of \emph{more and more sensitive} operations. 
This viewpoint, that we develop in the following sections, leads to the somehow unexpected discovery of a bridge between the metric and differential study of higher-order programs.
This connection not only suggest the application of optimization methods based on tropical mathematics to the study of the $\lambda$-calculus and its quantitative extensions, but it scales to a 
more abstract level, leading to introduce a 
differential operator for continuous functors between \emph{generalized} metric spaces (in the sense of \cite{Lawvere1973}).

>>>>

Yet, what if these polynomials were tropical ones, i.e.~piecewise linear functions? This way, eq.~\eqref{eq:taylor} could really be interpreted as a decomposition of $\lambda$-terms via Lipschitz maps. In other words, unbounded term application could be seen 
as a limit of \emph{more and more sensitive} operations.

This viewpoint, that we develop in the following sections, leads to the somehow unexpected discovery of a bridge between the metric and differential study of higher-order programs.
This connection not only suggests the application of optimization methods based on tropical mathematics to the study of the $\lambda$-calculus and its quantitative extensions, but it scales to a 
more abstract level, leading to introduce a 
differential operator for continuous functors between \emph{generalized} metric spaces (in the sense of \cite{Lawvere1973}).
